---
output: github_document
---

# Figures 
This script is used to create figures of the raw data. 
**Data was pre-processed to tidy format in the script data_prep.Rmd**

```{r}
#Load libraries 
library(dplyr)
library(tidyr)
library(ggplot2)
theme_set(theme_bw())

#Load in data 
load("tidy_df.Rdata")
```

Histogram of total alleles simulated for all simulation replicates to get an idea of the variation across replicates
```{r}
ggplot(tidy_df, aes(x=as.numeric(total_alleles))) +
    geom_bar() +
    ggtitle("Variation of total alleles simulated across replicates") +
    theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())
```

Scatter plot of all raw data obtained from resampling. Plots are faceted by maternal trees, and each color line represents a different pollen donor type. 
```{r}
#defining a color palette to use for the plots (color-blind accessible)
cbPalette <- c("#E69F00", "#56B4E9", "#CC79A7")

#defining more descriptive labels for the facets 
mat_tree_labs = c("1 maternal tree", "2 maternal trees", "5 maternal trees", "10 maternal trees", "25 maternal trees", "50 maternal trees", "100 maternal trees")
names(mat_tree_labs) = c("1", "2", "5", "10", "25", "50", "100")

tidy_df %>% 
    ggplot(aes(x=as.numeric(total_seeds), y=as.numeric(prop_capt), color=donor_type)) +
    geom_point(alpha=0.1) +
    facet_wrap(vars(maternal_trees), labeller = labeller(maternal_trees = mat_tree_labs)) +
    theme(strip.background = element_rect(color="black", fill="#F2F2F2", linetype="solid")) +
    ylim(0,1) + 
    ggtitle("Genetic diversity capture across all sampling scenarios") +
    ylab("Proportion of alleles captured") + 
    xlab("Total seeds sampled") + 
    scale_colour_manual(values=cbPalette)
```

Boxplots of some key scenarios for comparison: 
Genetic diversity capture for all scenarios with 200 total seeds sampled: 
```{r}
tidy_df %>% 
    filter(total_seeds==200) %>% 
    ggplot(aes(x=as.numeric(total_seeds), y=as.numeric(prop_capt), color=donor_type)) +
    geom_boxplot(alpha=0.25) +
    facet_wrap(vars(maternal_trees), labeller = labeller(maternal_trees = mat_tree_labs)) +
    theme(strip.background = element_rect(color="black", fill="#F2F2F2", linetype="solid")) +
    ylim(0,1) + 
    ggtitle("Genetic diversity capture for ideal scenarios with 200 total seeds sampled") +
    xlab("Donor type") +
    ylab("Proportion of alleles captured") +
    scale_colour_manual(values=cbPalette) +
    theme(axis.text.x=element_blank(),
          axis.ticks.x=element_blank())
```

Genetic diversity capture for all scenarios with 400 total seeds sampled: 
```{r}
tidy_df %>% 
    filter(total_seeds==400) %>% 
    ggplot(aes(x=as.numeric(total_seeds), y=as.numeric(prop_capt), color=donor_type)) +
    geom_boxplot(alpha=0.25) +
    facet_wrap(vars(maternal_trees), labeller = labeller(maternal_trees = mat_tree_labs)) +
    theme(strip.background = element_rect(color="black", fill="#F2F2F2", linetype="solid")) +
    ylim(0,1) + 
    ggtitle("Genetic diversity capture for ideal scenarios with 400 total seeds sampled") +
    xlab("Donor type") +
    ylab("Proportion of alleles captured") +
    scale_colour_manual(values=cbPalette) +
    theme(axis.text.x=element_blank(),
          axis.ticks.x=element_blank())
```