---
output: github_document
---

# Figures 
This script is used to create figures of the raw data. 
**Data was pre-processed to tidy format in the script data_prep.Rmd**

```{r}
#Load libraries 
library(dplyr)
library(tidyr)
library(ggplot2)
theme_set(theme_bw())

#Load in data 
load("tidy_df.Rdata")
```

Histogram of total alleles simulated for all simulation replicates to get an idea of the variation across replicates
```{r}
ggplot(tidy_df, aes(x=as.numeric(total_alleles))) +
    geom_bar() +
    ggtitle("Variation of total alleles simulated across replicates") +
    theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())
```

**Ideal Scenarios**  
  
Scatter plot of all raw data obtained from resampling. Plots are faceted by maternal trees, and each color line represents a different pollen donor type. 
```{r}
#defining a color palette to use for the plots (color-blind accessible)
cbPalette <- c("#E69F00", "#56B4E9", "#CC79A7")

#defining more descriptive labels for the facets 
mat_tree_labs = c("1 maternal tree", "2 maternal trees", "5 maternal trees", "10 maternal trees", "25 maternal trees", "50 maternal trees", "100 maternal trees")
names(mat_tree_labs) = c("1", "2", "5", "10", "25", "50", "100")

tidy_df %>% 
    ggplot(aes(x=as.numeric(total_seeds), y=as.numeric(prop_capt), color=donor_type)) +
    geom_point() +
    facet_wrap(vars(as.numeric(maternal_trees)), labeller = labeller(maternal_trees = mat_tree_labs)) +
    theme(strip.background = element_rect(color="black", fill="#F2F2F2", linetype="solid")) +
    ylim(0,1) + 
    ggtitle("Genetic diversity capture across all ideal sampling scenarios") +
    ylab("Proportion of alleles captured") + 
    xlab("Total seeds sampled") + 
    scale_colour_manual(values=cbPalette, labels = c("All eligible", "All same", "Skewed")) + 
    labs(color = "Donor Type")
```

Boxplots of some key scenarios for comparison: 
Genetic diversity capture for all scenarios with 200 total seeds sampled: 
```{r}
tidy_df %>% 
    filter(total_seeds==200) %>% 
    ggplot(aes(x=donor_type, y=as.numeric(prop_capt), color=donor_type)) +
    geom_boxplot() +
    facet_wrap(vars(as.numeric(maternal_trees)), labeller = labeller(maternal_trees = mat_tree_labs)) +
    theme(strip.background = element_rect(color="black", fill="#F2F2F2", linetype="solid")) +
    ylim(0,1) + 
    ggtitle("Genetic diversity capture for ideal scenarios with 200 total seeds sampled") +
    xlab("Donor type") +
    ylab("Proportion of alleles captured") +
    scale_colour_manual(values=cbPalette, labels = c("All eligible", "All same", "Skewed")) +
    theme(axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) + 
    labs(color = "Donor Type")
```

Genetic diversity capture for all scenarios with 400 total seeds sampled: 
```{r}
tidy_df %>% 
    filter(total_seeds==400) %>% 
    ggplot(aes(x=donor_type, y=as.numeric(prop_capt), color=donor_type)) +
    geom_boxplot() +
    facet_wrap(vars(as.numeric(maternal_trees)), labeller = labeller(maternal_trees = mat_tree_labs)) +
    theme(strip.background = element_rect(color="black", fill="#F2F2F2", linetype="solid")) +
    ylim(0,1) + 
    ggtitle("Genetic diversity capture for ideal scenarios with 400 total seeds sampled") +
    xlab("Donor type") +
    ylab("Proportion of alleles captured") +
    scale_colour_manual(values=cbPalette, labels = c("All eligible", "All same", "Skewed")) +
    theme(axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) + 
    labs(color = "Donor Type")
```
***   
  
**Realistic Scenarios**

```{r}
#Load in data
load("tidy_df_realistic.Rdata")
tidy_df_realistic = tidy_df
```

Plot all data together
```{r}
#defining a color palette to use for the plots (color-blind accessible)
cbPalette <- c("#E69F00", "#56B4E9", "#CC79A7")

#defining more descriptive labels for the facets 
mat_tree_labs = c("1 maternal tree", "2 maternal trees", "5 maternal trees", "10 maternal trees", "25 maternal trees", "50 maternal trees", "100 maternal trees")
names(mat_tree_labs) = c("1", "2", "5", "10", "25", "50", "100")

tidy_df_realistic %>% 
    ggplot(aes(x=as.numeric(total_seeds), y=as.numeric(prop_capt), color=donor_type)) +
    geom_point() +
    facet_wrap(vars(as.numeric(maternal_trees)), labeller = labeller(maternal_trees = mat_tree_labs)) +
    theme(strip.background = element_rect(color="black", fill="#F2F2F2", linetype="solid")) +
    ylim(0,1) + 
    ggtitle("Genetic diversity capture across all realistic sampling scenarios") +
    ylab("Proportion of alleles captured") + 
    xlab("Total seeds sampled") + 
    scale_colour_manual(values=cbPalette, labels = c("All eligible", "All same", "Skewed")) + 
    labs(color = "Donor Type")
```

Boxplots of scenarios with 200 seeds sampled total for comparison 
```{r}
tidy_df_realistic %>% 
    filter(total_seeds==200) %>% 
    ggplot(aes(x=donor_type, y=as.numeric(prop_capt), color=donor_type)) +
    geom_boxplot() +
    facet_wrap(vars(as.numeric(maternal_trees)), labeller = labeller(maternal_trees = mat_tree_labs)) +
    theme(strip.background = element_rect(color="black", fill="#F2F2F2", linetype="solid")) +
    ylim(0,1) + 
    ggtitle("Genetic diversity capture for realistic scenarios with 200 total seeds sampled") +
    xlab("Donor type") +
    ylab("Proportion of alleles captured") +
    scale_colour_manual(values=cbPalette, labels = c("All eligible", "All same", "Skewed")) +
    theme(axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) + 
    labs(color = "Donor Type")
```

400 seeds sampled total
```{r}
tidy_df_realistic %>% 
    filter(total_seeds==400) %>% 
    ggplot(aes(x=donor_type, y=as.numeric(prop_capt), color=donor_type)) +
    geom_boxplot() +
    facet_wrap(vars(as.numeric(maternal_trees)), labeller = labeller(maternal_trees = mat_tree_labs)) +
    theme(strip.background = element_rect(color="black", fill="#F2F2F2", linetype="solid")) +
    ylim(0,1) + 
    ggtitle("Genetic diversity capture for realistic scenarios with 400 total seeds sampled") +
    xlab("Donor type") +
    ylab("Proportion of alleles captured") +
    scale_colour_manual(values=cbPalette, labels = c("All eligible", "All same", "Skewed")) +
    theme(axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) + 
    labs(color = "Donor Type")
```

***  
  
**Comparing ideal and realistic scenarios directly**  
```{r}
load("tidy_df.Rdata")
#remove col to make same # cols 
tidy_df = subset(tidy_df, select = -c(seeds_per_tree))
#Create new columns to identify scenarios 
tidy_df$samp_type = "ideal"
tidy_df_realistic$samp_type = "realistic"
#Combine dataframes
combined_ideal_real = rbind(tidy_df, tidy_df_realistic)
```

Plotting scenarios with 200 seeds sampled total 
```{r}
combined_ideal_real %>%
    filter(total_seeds==200) %>%
    filter(maternal_trees>1) %>%
    ggplot(aes(x=donor_type, y=as.numeric(prop_capt), color=samp_type)) +
    geom_boxplot() +
    facet_wrap(vars(as.numeric(maternal_trees)), labeller = labeller(maternal_trees = mat_tree_labs)) +
    theme(strip.background = element_rect(color="black", fill="#F2F2F2", linetype="solid")) +
    ylim(0,1) + 
    ggtitle("Genetic diversity capture for scenarios with 200 total seeds sampled") +
    xlab("Donor type") +
    ylab("Proportion of alleles captured") +
    labs(color = "Sampling Type") +
    scale_x_discrete(labels=c("Eligible","Same","Skewed"))
```
